The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-15 src/tex/ms.tex
remove all inline \frac

Within this suite of codes, GridPolator has the added responsibility of binning spectra and producing wavelength axes that match those output by PSG. Wavelength sampling is done using a constant resolving power $R=\frac{\lambda}{\Delta \lambda}$. The binning algorithm takes a pair of high-resolution flux and wavelength arrays and resamples the flux to a lower-resolution wavelength axis. PSG specifies the central wavelength of each channel, and so this algorithm defines bin edges to be $\lambda_{\rm cen} \pm \frac{\lambda_{\rm cen}}{R}$.

>>>>

Within this suite of codes, GridPolator has the added responsibility of binning spectra and producing wavelength axes that match those output by PSG. Wavelength sampling is done using a constant resolving power $R=\lambda/{\Delta \lambda}$. The binning algorithm takes a pair of high-resolution flux and wavelength arrays and resamples the flux to a lower-resolution wavelength axis. PSG specifies the central wavelength of each channel, and so this algorithm defines bin edges to be $\lambda_{\rm cen} \pm {\lambda_{\rm cen}}/{R}$.
